Methodology for Assessing the State of the Practice for Domain X

### 2020-08-29 StateOfPractice/Methodology/Methodology.tex
updated 'Steps in Assessing Qualilty'

\section{Research Questions}

@@

\begin{enumerate}
\item Start with state of practice research questions.
\item Identify domain.  (Provide criteria on a candidate domain.)
\item Identify list of candidate software in the domain.  (Section~\ref{SecIdentifyCandSoft})
\item \emph{Domain Expert}: Vet domain software list.  
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})
\item \emph{Domain Expert}: Vet domain analysis
\item Measure using ``shallow'' measurement template.
\item Empirical measures.
\item Use AHP process to rank the software.  Tool for estimating AHP results?
  Tool for ranking and sorting by various criteria?  Conditional formula to
  assess software within each measure, or just use opinion of measurer?
\item Identify short list for deeper exploration.
\item \emph{Domain Expert}: vet AHP ranking and short list.
\item With short list:
\begin{enumerate}
\item Survey developers
\item Usability experiments
\item Performance benchmarks
\item Maintainability experiments
\end{enumerate}
\item Compare shallow and deep measures and ranking
\item Answers for research questions.
\end{enumerate}

@@

\section{Identify Candidate Software} \label{SecIdentifyCandSoft}

\begin{enumerate}
\item Must be open source.
\item Must have GitHub repository.
\end{enumerate}

@@

\section{Empirical Measures}

@@

@@

\subsection{Task selection criteria}
**The task selection will be determined with the aid of the domain expert attached to any of the selected projects.\\ 
**The domain expert will be asked to consider the below criteria when defining a task. \\
**Domain experts will also be asked to identify what background knowledge is necessary for the suggested tasks - Novice, Intermediate, Advanced
\begin {enumerate}
\item Collectively all tasks should not take no more than 2 hours.
\item Selected tasks should reflect common use cases of  the software.
\item Include tasks that require a set of sequential or hierarchical steps to be completed

@@

\section{Analytic Hierarchy Process}

Describe process.  Domain expert review.

>>>>

\section{Research Questions}\label{ResearchQuestions}

@@

\begin{enumerate}
\item Start with state of practice research questions. (Section~\ref{ResearchQuestions}) \pmi{To be completed}
\item Identify the domain. (Section~\ref{SecIdentifyDomain}) \pmi{To be completed}
\item \emph{Domain Experts}: Create a top ten list of software packages in the domain. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Brief the Domain Experts on the overall objective, research proposal, research questions, measurement template, survey for short list projects, usability tests, performance benchmarks, maintainability experiments. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Identify broad list of candidate software packages in the domain. (Section~\ref{SecIdentifyCandSoft}) \pmi{To be completed}
\item Preliminary filter of software packages list. (Section~\ref{SecInitialFilter}) \pmi{To be completed}
\item \emph{Domain Experts}: Review domain software list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})\pmi{To be completed}
\item \emph{Domain Experts}: Vet domain analysis. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item Gather source code and documentation for each prospective software package.
\item Collect empirical measures. (Section~\ref{SecEmpiricalMeasures}) \pmi{To be completed}
\item Measure using ``shallow'' measurement template. (Section~\ref{SecShallowMeasure}) \pmi{To be completed}
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP}) \pmi{To be completed}
\item Identify a short list of top software packages, typically four to six, for deeper exploration according to the AHP rankings of the shallow measurements.
\item \emph{Domain Experts}: Vet AHP ranking and short list. (\href{run:Meeting Agenda with Domain Experts.pdf}{Meeting Agenda with Domain Experts}) \pmi{This was part of the original Steps in Assessing Quality list. We need to add it to the Meeting Agenda}
\item With short list:
\begin{enumerate}
\item Survey developers \pmi{To do: Link to survey}
\item Usability experiments \pmi{Move the below usability section to a new doc, and link to it.}
\item Performance benchmarks\pmi{note: this is still in consideration}
\item Maintainability experiments\pmi{note: this is still in consideration}
\end{enumerate}
\item Rank short list. (Section~\ref{SecRankShortList}) \pmi{To be completed}
\item Document answers for research questions.
\end{enumerate}

@@

\section{How to Identify the Domain} \label{SecIdentifyDomain}
\begin{enumerate}
	\item Needs to be "a community of"/many people using and studying this domain
	\item There needs to be "many" software solutions
	\item There needs to be a user community using these solutions
	\item Must be in the research software scope
	\item Specific enough scope
	\item Must be a well understood domain / mature
\end{enumerate}

\section{How to Identify Candidate Software} \label{SecIdentifyCandSoft}
\pmi{outline here how to find such a list}
\begin{enumerate}
\item Must have viewable source code.
\item Ideally have a git repository. \pmi{Not all of mine had this..}
\end{enumerate}

\section{How to Initially Filter the Software List} \label{SecInitialFilter}
The person doing this must keep track of both the initial and filtered lists. The reasons for this is traceability bc..
\begin{enumerate}
	\item Professionalism..
	\item Available documentation..
	\item Status..
	\item Availability of source code..
\end{enumerate}

@@

\section{Empirical Measures} \label{SecEmpiricalMeasures}

@@

\section{Measure Using Shallow Measurement Template} \label{SecShallowMeasure}
This step...
The measurement template can be found \href{run:Combined_MeasurementTemplate_EmpiricalMeasures.xlsx}{here}.
\begin{enumerate}
	\item Step 1..
\end{enumerate}

@@

\subsection{Task selection criteria}
**The task selection will be determined with the aid of the domain experts attached to any of the selected projects.\\ 
**The domain experts will be asked to consider the below criteria when defining a task. \\
**Domain experts will also be asked to identify what background knowledge is necessary for the suggested tasks - Novice, Intermediate, Advanced
\begin {enumerate}
\item Collectively all tasks should not take no more than 2 hours.
\item Selected tasks should reflect common use cases of  the software.
\item Include tasks that require a set of sequential or hierarchical steps to be completed

@@

\section{Analytic Hierarchy Process} \label{SecAHP}

Describe process. Domain experts review. Outline the tool we used. The README file of the tool can be found \href{run:../AHP2020/LBM/README.txt}{here}.

\section{Rank Short List} \label{SecRankShortList}
Rank using pairwise comparison of short list results.
\begin{enumerate}
	\item Compare with respect to usability
	\item ...
\end{enumerate}
